---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oEmbed

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/oEmbed)](https://CRAN.R-project.org/package=oEmbed)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of oEmbed is to make a request for web resources that follows the '[oEmbed](https://oembed.com)' specification and display the content in R.

## Installation

You can install the released version of oEmbed from GitHub using remotes package:

``` r
if (!requireNamespace("remotes"))
  install.packages("remotes")

remotes::install_github("uribo/oEmbed")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(oEmbed)
## basic example code
```

```{r, echo=TRUE, eval=FALSE}
x <- 
  oembed(service = "twitter", 
         url = "https://twitter.com/u_ribo/status/1318770949722759168")
x
```

```{r, echo=FALSE, eval=TRUE}
x <- 
  list(
  url = "https://twitter.com/u_ribo/status/1318770949722759168",
  author_name = "Uryu Shinya",
  author_url = "https://twitter.com/u_ribo",
  html = "<blockquote class=\"twitter-tweet\"><p lang=\"ja\" dir=\"ltr\">Rでのモデル開発を統一的に行う、tidymodelsの情報を整理しました\U0001f4aa <br>{tune}や{workflows}によるパラメータ探索、ワークフローの運用の話まで、広く紹介します。<br>{recipes}で新しいstep_()や関連パッケージも増えて更に便利になりました。<br>\U0001f989コード <a href=\"https://t.co/sT9jhrwaK8\">https://t.co/sT9jhrwaK8</a> <a href=\"https://t.co/Ag1CNutEBI\">https://t.co/Ag1CNutEBI</a> <a href=\"https://t.co/dMejxP6mwd\">pic.twitter.com/dMejxP6mwd</a></p>&mdash; Uryu Shinya (@u_ribo) <a href=\"https://twitter.com/u_ribo/status/1318770949722759168?ref_src=twsrc%5Etfw\">October 21, 2020</a></blockquote>\n<script async src=\"https://platform.twitter.com/widgets.js\" charset=\"utf-8\"></script>\n",
  width = 550L,
  height = NULL,
  type = "rich",
  cache_age = "3153600000",
  provider_name = "Twitter",
  provider_url = "https://twitter.com",
  version = "1.0"
)
x
```


```{r, echo = TRUE}
embed_contents(x)
```

### Video

Browsing YouTube Videos in RStudio Viewer

```{r, echo = TRUE, eval = FALSE}
x <-
  oembed("youtube", 
       url = "https://www.youtube.com/watch?v=wQPgM-9LatM", 
       format = "json",
       maxwidth = 600)

htmltools::browsable(embed_contents(x))
```


## Similar Projects

- [vembedr](https://github.com/ijlyttle/vembedr)
- [tubeplayR](https://github.com/kazutan/tubeplayR)
